### 2013-10-22 NeurounitFrontiers/Paper.tex
Added acknowledgements

\begin{figure}%{r}{0.6\textwidth}
%\vspace{-38px}
\includegraphics[scale=0.75]{sciunit_overview.pdf}
\caption{Proposal overview. 
\small{i) The \textit{SciUnit} framework can generate discipline-specific libraries for tests generation and model interfacing.  
\textit{NeuronUnit} is proposed and described here.  Experimental data guides test development; model generation informs and is informed by these \textit{SciUnit} libraries.  
Each \text{SciUnit} test suite repository on GitHub is indexed by the \textit{SciDash} web application.  
Test suites for OSB and QSNMC (described in the text) are being built. 
\textit{SciDash} automatically runs the test collections in each suite and publicly displays the results.}}
%\vspace{-10px}
\label{fig:sciunit_overview}
\end{figure}
\leavevmode
\vspace{-0px}
Each of these examples leveraged \emph{ad hoc} infrastructure. Although the specific criteria used to evaluate models varies widely between disciplines in neuroscience, the underlying test-driven methodology has many common features that can be implemented once. Recognizing this, we have developed a discipline-agnostic framework for developing scientific model validation test suites called \textit{SciUnit}\cite{sciunit_url}. To demonstrate the power of this framework in combination with existing neuroinformatics tools, we developed \textit{NeuronUnit\-}, which allows scientists to build \textit{SciUnit} tests that validate neural models described using the  \text{NeuroML} modeling standard against electrophysiological data collected by the \textit{NeuroElectro Project} \cite{neuroelectro_url}, leveraging facilities from the \textit{NeuroTools} project to..\todo{what does NeuroTools do?}.% In addition to this open testing toolkit we also provide a library of tests for models of spiking single neurons.

@@

>>>>

\begin{figure}%{r}{0.6\textwidth}
%\vspace{-38px}
\includegraphics[scale=0.75]{sciunit_overview.pdf}
\caption{Proposal overview. 
\small{i) The \textit{SciUnit} framework can generate discipline-specific libraries for tests generation and model interfacing.  
\textit{NeuronUnit} is proposed and described here.  Experimental data guides test development; model generation informs and is informed by these \textit{SciUnit} libraries.  
Each \text{SciUnit} test suite repository on GitHub is indexed by the \textit{SciDash} web application.  
Test suites for OSB and QSNMC (described in the text) are being built. 
\textit{SciDash} automatically runs the test collections in each suite and publicly displays the results.}}
%\vspace{-10px}
\label{fig:sciunit_overview}
\end{figure}
\leavevmode
\vspace{-0px}
Each of these examples leveraged \emph{ad hoc} infrastructure. Although the specific criteria used to evaluate models varies widely between disciplines in neuroscience, the underlying test-driven methodology has many common features that can be implemented once. Recognizing this, we have developed a discipline-agnostic framework for developing scientific model validation test suites called \textit{SciUnit}\cite{sciunit_url}. To demonstrate the power of this framework in combination with existing neuroinformatics tools, we developed \textit{NeuronUnit\-}, which allows scientists to build \textit{SciUnit} tests that validate neural models described using the  \text{NeuroML} modeling standard against electrophysiological data collected by the \textit{NeuroElectro Project} \cite{neuroelectro_url}, leveraging facilities from the \textit{NeuroTools} project to..\todo{what does NeuroTools do?}.\todo{This is what NeuronUnit can do now, but it is not in principle limited to this.  I would rather have this pipeline be described in the results as one thing that is fully implemented, but not limit ourselves to this in the introduciton.}% In addition to this open testing toolkit we also provide a library of tests for models of spiking single neurons.

@@

\section{Acknowledgements}
This work was supported in part by grant R01MH081905 from the National Institute of Mental Health. The content is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.
